Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Minor tweaks to section

```{julia}
#| include: false

cd("../src")
include("../src/common.jl")

@@

The spatial extent of GBR coral reefs used in this investigation includes 3806 reef areas.
It follows the reef definitions as provided by the Great Barrier Reef Marine Park Authority
\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
Annually and spatially averaged Degree Heating Week (DHW) data is used to represent future
thermal stress at each reef location. Five Global Climate Models (GCMs) (EC-Earth3-Veg,
ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and GDFL-CM4) from the Sixth Phase of the Coupled
Model Intercomparison Project (CMIP6; **citation**) were selected for this study.
Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great
Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. These GCMs were selected from available GCMs downscaled by Dixon
et al. [-@dixon] based on evaluation by Grose et al. [-@grose2023], which found high
correlation between observed temperature, rainfall, El Niño Southern Oscillation and Indian
Ocean Dipole patterns in the Australian terrestrial region, and the corresponding mechanisms
in these GCMs. Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long
term warming caused by a doubling of carbon dioxide above its pre-industrial concentration
[@forster2021]. The four GCMs span a range of ECS values within the IPCC assessed likely
range, and GCM development families, allowing for a range of possible climate futures to be
explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
[@grose2023; @shepherd2018]). The following analyses are performed using each GCM
separately. SSP 2-4.5 is used as a plausible emission pathway under current emission
trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
IPCC -@climate2023].

>>>>

```{julia}
#| include: false
cd("../src")
include("../src/common.jl")

@@

The spatial extent of the GBR coral reefs represented in this investigation follows the reef
definitions available via the Great Barrier Reef Marine Park Authority
\[https://geohub-gbrmpa.hub.arcgis.com/datasets/GBRMPA::great-barrier-reef-features-/explore?location=-19.221541%2C145.776418%2C4.94\].
In total this covers 3806 reef areas across the GBR marine park. Annually and spatially
averaged Degree Heating Week (DHW) data was used to represent future thermal stress at each
reef location.

Statistically downscaled 1km resolution Sea Surface Temperature (SST) data for the Great
Barrier Reef were obtained from the HighResCoralStress database [@dixon2022; @dixon].
Maximum monthly mean DHW levels were calculated from the SST data following NOAA methodology
[@liu2017; @skirving2020]. The SSTs are represented by a selection of five Global Climate
Models (GCMs) from the Sixth Phase of the Coupled Model Intercomparison Project (CMIP6;
**citation**). These five GCMs were EC-Earth3-Veg, ACCESS-CM2, ACCESS-ESM1-5, NorESM2-MM and
GDFL-CM4, and their inclusion were based on evaluation by Grose et al. [-@grose2023], which
found high correlation between observed temperature, rainfall, El Niño Southern Oscillation
and Indian Ocean Dipole patterns in the Australian terrestrial region, and the corresponding
mechanisms in these GCMs.

Equilibrium climate sensitivity (ECS) is defined, by the IPCC, as the long term warming
caused by a doubling of carbon dioxide above its pre-industrial concentration
[@forster2021]. The four GCMs span a range of ECS values within the IPCC assessed likely
range, and GCM development families, allowing for a range of possible climate futures to be
explored, capturing the uncertainty in future responses to CO2 increases (@fig-ecs;
[@grose2023; @shepherd2018]). The following analyses are performed using each GCM
separately. SSP 2-4.5 is used as a plausible emission pathway under current emission
trajectories, with similar atmospheric CO2 levels remaining until 2050 [@hausfather2020;
IPCC -@climate2023].
